\chapter{Module guide}\label{chap:modules}

This chapter records the intended role of each main Lean file.

\section{Public files}

\begin{itemize}
\item \textbf{\texttt{ConvexSubgaussian/GaussianMain.lean}}:
  the theorem-facing endpoint file. This is the file a reader should open first.
\item \textbf{\texttt{ConvexSubgaussian/GaussianAsymptotics.lean}}:
  the public support layer exposing the explicit constants and the two public
  comparison theorems used by the endpoint file.
\item \textbf{\texttt{ConvexSubgaussian/CoreDefs.lean}}:
  project-level definitions such as the hinge function, stop-loss transform, and
  the random-variable version of the sub-Gaussian tail condition.
\item \textbf{\texttt{ConvexSubgaussian.lean}}:
  the umbrella import for the public package.
\end{itemize}

\section{Internal proof file}

\begin{itemize}
\item \textbf{\texttt{ConvexSubgaussian/Internal/GaussianProof.lean}}:
  the analytic proof body. This file contains the layer-cake lemmas, the
  envelope construction, the Gaussian closed-form calculations, the monotone
  ratio argument, the construction of the extremal measure, and the reduction
  from stop-loss comparison to arbitrary convex test functions.
\end{itemize}

\section{Reading order}

\begin{itemize}
\item Start with \texttt{GaussianMain.lean} for the final theorem.
\item Then read \texttt{GaussianAsymptotics.lean} for the explicit constant
  and the public domination/sharpness split.
\item Use this blueprint to navigate the internal route in
  \texttt{Internal/GaussianProof.lean}.
\end{itemize}
