\chapter{Setup and endpoint constants}\label{chap:setup}

\section{Reader-facing theorem surface}

The public Lean API is built around the random-variable formulation of the
comparison problem. The endpoint file exposes the admissible Gaussian scales
and their infimum.

\begin{definition}[Endpoint quantities]\label{def:endpoint}
\lean{AdmissibleScale}\leanok
\lean{cStar}\leanok
The declaration \texttt{AdmissibleScale} says that a positive number $c$ is
admissible if every centered real random variable $X$ with the two-sided tail
bound
\[
  \Prb(|X| > t) \le 2 e^{-t^2/2} \qquad (t \ge 0)
\]
is convex-dominated by the centered Gaussian law of standard deviation $c$.
The quantity $c_\star$ is then defined as the infimum of all such admissible
scales.
\end{definition}

\begin{definition}[Explicit Gaussian comparison constants]\label{def:constants}
\lean{t0}\leanok
\lean{A}\leanok
\lean{B}\leanok
\lean{a}\leanok
\lean{p0}\leanok
\lean{z}\leanok
\lean{c0}\leanok
\lean{gaussianScale}\leanok
The explicit constant is built from the sub-Gaussian tail cap
\[
  s_G(t) := \min\{1, 2e^{-t^2/2}\}, \qquad
  t_0 := \sqrt{2 \log 2},
\]
the total tail mass
\[
  A := \int_0^\infty s_G(t)\,dt, \qquad B := A/2,
\]
the unique threshold $a > t_0$ solving
\[
  H(a) = a s_G(a) + \int_a^\infty s_G(t)\,dt = B,
\]
the height $p_0 := s_G(a)$, the Gaussian tail quantile $z$ satisfying
$\overline{\Phi}(z) = p_0$, and finally
\[
  c_0 := \frac{B}{\varphi(z)}.
\]
The public support file exposes these definitions exactly so the reader can see
which constant is being proved optimal.
\end{definition}

\section{Comparison and sharpness statements}

The endpoint theorem is assembled from one comparison statement and one
sharpness statement.

\begin{theorem}[Named comparison and sharpness results]\label{thm:public-support}
\lean{gaussianDomination_c0}\leanok
\lean{gaussianSharpness_below_c0}\leanok
The theorem \texttt{gaussianDomination\_c0} is the comparison statement at the
optimal Gaussian scale: it shows that the Gaussian law at scale $c_0$
dominates every admissible random variable against every convex integrable test
function. The theorem
\texttt{gaussianSharpness\_below\_c0} proves that every smaller positive scale
$c < c_0$ fails already for the canonical witness measure $\mu^\star$ and a
hinge test function of the form $x \mapsto (x-u)_+$.
\end{theorem}

\begin{proof}\leanok
The proof infrastructure for these two statements lives in the internal analytic
module. The public wrapper \texttt{gaussianDomination\_c0} pushes a random
variable $X$ forward to its law, checks the mean-zero and tail hypotheses on
that law, and then invokes the internal measure-theoretic domination theorem.
The public sharpness theorem packages the explicit extremal witness already
constructed in Lean and rewrites its stop-loss strictness into the reader-facing
hinge-integral inequality.
\end{proof}
